---
title: "emulating code-line-numbers"
format:
  revealjs:
    width: 1280
    height: 720
filters:
  - code-line-style
pagetitle: code-line-style — emulating code-line-numbers
echo: false
code-line-numbers: false
---

## Why?

Quarto's built-in `code-line-numbers` is the common-case shortcut for "fade
in some lines as I talk." `code-line-style` is a superset — same look from the
`mark` style in the `emphasis` preset.

The mapping is one-for-one. Reach for `code-line-style` when you outgrow it
(custom colors, multiple styles per step, the diff preset, labels…).

## The built-in for reference

````markdown
```{{r}}
#| code-line-numbers: "3-5"
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```
````

```{r}
#| echo: true
#| eval: false
#| code-line-numbers: "3-5"
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Range — `code-line-numbers="3-5"`

````markdown
```{.r data-code-line-style="mark:3-5" data-code-line-style-preset="emphasis"}
df |>
  ...
```
````

```{.r data-code-line-style="mark:3-5" data-code-line-style-preset="emphasis"}
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Disparate lines — `code-line-numbers="2,4"`

````markdown
```{.r data-code-line-style="mark:2, mark:4" data-code-line-style-preset="emphasis"}
df |>
  ...
```
````

```{.r data-code-line-style="mark:2, mark:4" data-code-line-style-preset="emphasis"}
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Progressive — `code-line-numbers="|3|4-5"`

````markdown
```{.r data-code-line-style="|mark:3|mark:4-5" data-code-line-style-preset="emphasis"}
df |>
  ...
```
````

Press → to walk through.

```{.r data-code-line-style="|mark:3|mark:4-5" data-code-line-style-preset="emphasis"}
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Where `code-line-style` goes further

You can pick a different color, stack styles, or attach a label — things
`code-line-numbers` can't do:

````markdown
```{{r}}
#| code-line-style:
#|   styles:
#|     warn: { bg: "#ffd4d4", gutter: "#c00", marker: "!" }
#|   steps:
#|     - mark: 2
#|     - warn: { line: 4, label: "this is the bottleneck" }
```
````

```{r}
#| echo: true
#| eval: false
#| code-line-style:
#|   preset: emphasis
#|   styles:
#|     warn: { bg: "#ffd4d4", gutter: "#c00", marker: "!" }
#|   steps:
#|     - mark: 2
#|     - warn: { line: 4, label: "this is the bottleneck" }
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```
