---
title: "custom styles"
format:
  revealjs:
    width: 1280
    height: 720
filters:
  - code-style
pagetitle: code-style — custom
echo: false
code-line-numbers: false
---

## Inline custom styles

Define styles in the cell option and apply them by name. No preset needed.

````markdown
```{{r}}
#| code-style:
#|   styles:
#|     warn:  { bg: "#fff3bf", gutter: "#f08c00", marker: "!" }
#|     ghost: { opacity: 0.35 }
#|   steps:
#|     - warn: 3
#|     - ghost: 1-2
```
````

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   styles:
#|     warn:   { bg: "#fff3bf", gutter: "#f08c00", marker: "!" }
#|     ghost:  { opacity: 0.35 }
#|   steps:
#|     - warn: 3
#|     - ghost: 1-2
mtcars |>
  dplyr::filter(cyl == 6) |>
  dplyr::group_by(gear) |>
  dplyr::summarise(m = mean(mpg)) |>
  dplyr::arrange(dplyr::desc(m))
```

## Composing styles

A line can be targeted by multiple styles in the same step. Non-conflicting
properties stack; conflicting properties use spec order — later wins.

````markdown
```{{r}}
#| code-style:
#|   styles:
#|     bold-line: { weight: bold }
#|   steps:
#|     - hi: 3
#|       bold-line: 3
```
````

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   styles:
#|     bold-line: { weight: bold }
#|   steps:
#|     - hi: 3
#|       bold-line: 3
mtcars |>
  dplyr::filter(cyl == 6) |>
  dplyr::group_by(gear) |>
  dplyr::summarise(m = mean(mpg)) |>
  dplyr::arrange(dplyr::desc(m))
```

## Dev-mode errors

Append `?cs-debug=1` to the page URL to see inline error banners for unknown
style names, bad ranges, or malformed specs. In production, errors only log
to the console.
