---
title: "transitions"
format:
  revealjs:
    width: 1280
    height: 720
filters:
  - code-style
pagetitle: code-style — transitions
echo: false
code-line-numbers: false
---

## Default transition (200ms ease)

Press → to step through.

```{.r data-code-style="|hi:2|hi:3|hi:4-5"}
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Slow + ease-out (block level)

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   transition: { duration: 800, easing: ease-out }
#|   steps:
#|     - hi: 2
#|     - hi: 3
#|     - hi: 4-5
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Per-step transition

Each step picks its own timing.

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   steps:
#|     - hi: 2
#|       transition: { duration: 200 }
#|     - hi: 3
#|       transition: { duration: 1000, easing: ease-in-out }
#|     - hi: 4-5
#|       transition: { duration: 200 }
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Per-style transition

A custom style can carry its own timing.

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   styles:
#|     slow-focus: { bg: "#fff3bf", duration: 1200, easing: ease-out }
#|   steps:
#|     - slow-focus: 3
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Named transition modes

`mode: none | fade | slide | wipe | morph`.

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   transition: { mode: slide, duration: 500 }
#|   steps:
#|     - hi: 2
#|     - hi: 3
#|     - hi: 4-5
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```

## Presence: lines enter and exit

The `diff` preset's `add` and `rem` carry presence semantics. `add` lines
slide in from height 0; `rem` lines collapse out.

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   transition: { duration: 600 }
#|   steps:
#|     - rem: 3-5
#|     - add: 3-6
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(
    m = mean(mpg),
    .by = gear
  ) |>
  arrange(desc(m))
```

## Mode per step

```{r}
#| echo: true
#| eval: false
#| code-style:
#|   steps:
#|     - hi: 2
#|       transition: { mode: fade }
#|     - hi: 3
#|       transition: { mode: wipe, duration: 600 }
#|     - hi: 4-5
#|       transition: { mode: morph }
df |>
  filter(cyl == 6) |>
  group_by(gear) |>
  summarise(m = mean(mpg)) |>
  arrange(desc(m))
```
